{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
removed trailing whitespaces
addded introduction to the type system
introduced sequential type system

\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}

>>>>

\subsection{Type system}
\label{sec:typesystem}
The type system is the core part of the framework in the effect that it
enforces the previously defined noninterference property. Thus every
program which is typable, is noninterfering.

The type system for multithreaded programs is build up from a type system
for sequential programs for which the following assumptions hold:

\begin{enumerate}
\item We have a partial ordered set $(LType, \leq)$ of local types
\item and typing judgments of the form $se, i \vdash_{seq} s \Rightarrow t$, where
$s, t \in LType$, $i \in \mathcal{P}$ and se is a securirty environment.
\end{enumerate}

This type system is extended by the following rules, to support multithreading:

\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}
